---
title: "2024"
execute:
  message: false
  warning: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(DBI)
library(tictoc)

xaringanExtra::use_panelset()
```

```{r}
#| label: index-table
#| echo: false

challenge_done <- fs::dir_ls("./2024/", recurse = TRUE) |>
  str_subset("query") |>
  str_extract("(?<=query_day)(.*)(?=.sql)") |>
  as.numeric()

not_done <- setdiff(seq(25), challenge_done)

htmltools::tags$style(
  str_c(collapse = "\n",
    c(
      glue::glue(
        "#panelset_001_day-[challenge_done] {color: #409327 !important;}",
        .open = "[", .close = "]"
      ),
      glue::glue(
        "#panelset_001_day-[not_done] {color: #D63131 !important;}",
        .open = "[", .close = "]"
      )
    )
  )
)
```

```{r}
#| label: connect-db
#| echo: false

con <- DBI::dbConnect(RPostgres::Postgres(),
    host=Sys.getenv("DBHOST"),
    port=Sys.getenv("DBPORT"),
    user=Sys.getenv("DBUSER"),
    password=Sys.getenv("DBPASS"),
    dbname=Sys.getenv("DBNAME"),
)

knitr::opts_chunk$set(connection = "con")
```

:::: {.panelset}

::: {.panel}

## Day 1 {.panel-name}

**Day 1**

```{r, code=readLines("./2024/day_01/query_day01.sql")}
#| label: code-day01
#| eval: false
```

```{r}
#| label: day01
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_01/query_day01.sql")))
toc()
```

:::

::: {.panel}

# Day 2 {.panel-name}


**Day 2**

```{r, code=readLines("./2024/day_02/query_day02.sql")}
#| label: code-day02
#| eval: false
```

```{r}
#| label: day02
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_02/query_day02.sql")))
toc()
```

:::

::: {.panel}

# Day 3 {.panel-name}

**Day 3**

```{r, code=readLines("./2024/day_03/query_day03.sql")}
#| label: code-day03
#| eval: false
```

```{r}
#| label: day03
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_03/query_day03.sql")))
toc()
```

:::

::: {.panel}

# Day 4 {.panel-name}

**Day 4**

```{r, code=readLines("./2024/day_04/query_day04.sql")}
#| label: code-day04
#| eval: false
```

```{r}
#| label: day04
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_04/query_day04.sql")))
toc()
```

:::

::: {.panel}

# Day 5 {.panel-name}

**Day 5**

```{r, code=readLines("./2024/day_05/query_day05.sql")}
#| label: code-day05
#| eval: false
```

```{r}
#| label: day05
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_05/query_day05.sql")))
toc()
```

:::

::: {.panel}

# Day 6 {.panel-name}

**Day 6**

```{r, code=readLines("./2024/day_06/query_day06.sql")}
#| label: code-day06
#| eval: false
```

```{r}
#| label: day06
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_06/query_day06.sql")))
toc()
```

:::

::: {.panel}

# Day 7 {.panel-name}

**Day 7**

```{r, code=readLines("./2024/day_07/query_day07.sql")}
#| label: code-day07
#| eval: false
```

```{r}
#| label: day07
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_07/query_day07.sql")))
toc()
```

:::

::: {.panel}

# Day 8 {.panel-name}

**Day 8**

```{r, code=readLines("./2024/day_08/query_day08.sql")}
#| label: code-day08
#| eval: false
```

```{r}
#| label: day08
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_08/query_day08.sql")))
toc()
```

:::

::: {.panel}

# Day 9 {.panel-name}

**Day 9**

```{r, code=readLines("./2024/day_09/query_day09.sql")}
#| label: code-day09
#| eval: false
```

```{r}
#| label: day09
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_09/query_day09.sql")))
toc()
```

:::

::: {.panel}

# Day 10 {.panel-name}

**Day 10**

```{r, code=readLines("./2024/day_10/query_day10.sql")}
#| label: code-day10
#| eval: false
```

```{r}
#| label: day10
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_10/query_day10.sql")))
toc()
```

:::

::: {.panel}

# Day 11 {.panel-name}

**Day 11**

```{r, code=readLines("./2024/day_11/query_day11.sql")}
#| label: code-day11
#| eval: false
```

```{r}
#| label: day11
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_11/query_day11.sql")))
toc()
```

:::

::: {.panel}

# Day 12 {.panel-name}

**Day 12**

```{r, code=readLines("./2024/day_12/query_day12.sql")}
#| label: code-day12
#| eval: false
```

```{r}
#| label: day12
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_12/query_day12.sql")))
toc()
```

:::

::: {.panel}

# Day 13 {.panel-name}

**Day 13**

```{r, code=readLines("./2024/day_13/query_day13.sql")}
#| label: code-day13
#| eval: false
```

```{r}
#| label: day13
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_13/query_day13.sql")))
toc()
```

:::

::: {.panel}

# Day 14 {.panel-name}

**Day 14**

```{r, code=readLines("./2024/day_14/query_day14.sql")}
#| label: code-day14
#| eval: false
```

```{r}
#| label: day14
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_14/query_day14.sql")))
toc()
```

:::

::: {.panel}

# Day 15 {.panel-name}

**Day 15**

```{r, code=readLines("./2024/day_15/query_day15.sql")}
#| label: code-day15
#| eval: false
```

```{r}
#| label: day15
#| echo: false
#| cache: true

tic()
print(dbGetQuery(con, statement = read_file("./2024/day_15/query_day15.sql")))
toc()
```

:::

::: {.panel}

# Day 16 {.panel-name}

:::

::: {.panel}

# Day 17 {.panel-name}

:::

::: {.panel}

# Day 18 {.panel-name}

:::

::: {.panel}

# Day 19 {.panel-name}

:::

::: {.panel}

# Day 20 {.panel-name}

:::

::: {.panel}

# Day 21 {.panel-name}

:::

::: {.panel}

# Day 22 {.panel-name}

:::

::: {.panel}

# Day 23 {.panel-name}

:::

::: {.panel}

# Day 24 {.panel-name}

:::

::: {.panel}

# Day 25 {.panel-name}

:::

::::
